Codebook
========
Variable list and descriptions
------------------------------

Variable name     | Description
------------------|------------
Subject.ID        | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
Activity          | Activity name
featureGatherType | Feature: Time domain signal or frequency domain signal (Time or Freq)
featureInstrument | Feature: Measuring instrument (Accelerometer or Gyroscope)
accelarationSignal| Feature: Acceleration signal (Body or Gravity)
featureValueType  | Feature: Variable (Mean or SD)
isJerkSignal      | Feature: Jerk signal
isEuclideanNorm   | Feature: Is feature Magnitude of the signals calculated using the Euclidean norm
featureAxis       | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featAverage       | Feature: Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
data.root <- "C:/Dev/Src/Coursera_DataScience/Getting_Clearning_Data/course_project/GetCleanDataCourseProject/UCI HAR Dataset"
dfTidy <- read.table(file.path(data.root, "output.txt"), header = TRUE)
str(dfTidy)
```

List the key variables in the data table
----------------------------------------

```{r}
colnames(dfTidy)
```

Show a few rows of the dataset
------------------------------

```{r}
head(dfTidy)
```

Summary of variables
--------------------

```{r}
summary(dfTidy)
```
